Untitled

### 2021-08-14 Main_Figures/Traits_Table.Rmd
journal abbreviations of refs

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=14}
setwd("~/R_Projects/Reproductive Traits")

@@

dat <- data.frame(Type, Trait,Number_of_records_quantitative,Type_1, Trait1, T.cat,Number_of_records_categorical)

colnames(dat) <- c("Type","Traits", "Records","Type", "Traits", "Categories", "Records")

kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c")) %>%
kable_styling(full_width = T) %>%
add_header_above(c("Quantitative traits" = 3,"Categorical traits" = 4),bold=T)  %>%
    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=5, fig.width=8}
setwd("~/R_Projects/Reproductive Traits")

@@

colnames(dat) <- c("Type","Traits","Type", "Traits", "Categories")

kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c")) %>%
kable_styling(full_width = F)
